{\fontsize{100}{120}\selectfont Real-Time Activity Classification by Matched Filtering Using Body-Worn Accelerometers}

### 2016-11-14 notes/poster/poster.tex
Incrementals to the poster

Because training module does not need to be performed in real time, this can be performed on an external device such as a smart phone or tablet where processing resources are in greater abundance.
Training the module creates the reference signals to be used on the microcontroller for the real-time activity classification processing.

@@

%%%%%%%%%%%%%%%
% Performance %
%%%%%%%%%%%%%%%
\section{Performance}
The Kinetisense sensor was used for the algorithm performance analysis.
This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
A separate instance of walking data was used specifically for training the classifier.

>>>>

Because training module does not need to be performed in real time, this can be done on an external device such as a smart phone or tablet where processing resources are in greater abundance.
Training the module creates the reference signals to be used on the microcontroller for the real-time activity classification processing.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Performance Assessment %
%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Performance Assessment}
The Kinetisense sensor was used for the algorithm performance assessment.
This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
A separate instance of walking data was used specifically for training the classifier.
